# Metrics

Various metrics on my data

Sites with the most available aerial imagery
```{r most aerial, eval = TRUE, echo = TRUE}
number<-aerial%>%
  filter(year!='NA')%>%
  group_by(Fire_name) %>% 
  tally() %>% 
  arrange(desc(n))
```
First and last years of data
```{r range aerial, eval = TRUE, echo = TRUE}
range<-aerial%>%
    group_by(Fire_name) %>%
    filter(year!='NA')%>%
    summarize(min_year=min(year),
              max_year=max(year))
```

Site with the greatest frequency of imagery
```{r frequency aerial, eval = TRUE, echo = TRUE}
range%>%
  filter(min_year != "") %>% 
  mutate(range=as.numeric(max_year)-as.numeric(min_year)+1) %>% 
  left_join(number, by="Fire_name") %>% 
  mutate(freq_per_yr=n/range) %>% 
  mutate(freq_per_yr=round(freq_per_yr,1)) %>% 
  arrange(desc(freq_per_yr))
```
We can see that Box Canyon and Pole Creek have the most available imagery for their time period and will have the highest temporal resolution for analysis.


Wood Features broken down as individual pieces and jams
```{r count of wood, eval = TRUE, echo = TRUE}
woodnumber<-lw_data%>%
  mutate(Feature_type = case_when(
    Quantity=="1" ~ "Individual Piece",
    TRUE ~ "Wood Jam")) %>% 
  group_by(Feature_type) %>% 
  tally()
```
Wood Features broken down by amount of wood in each type
```{r amount of wood, eval = TRUE, echo = TRUE}
woodamount<-lw_data%>%
  mutate(Feature_type = case_when(
    Quantity=="1" ~ "Individual Piece",
    TRUE ~ "Wood Jam")) %>%
  group_by(Feature_type) %>% 
  summarize(sumQ=sum(as.numeric(Quantity)))
```
```{r compare, eval = TRUE, echo = TRUE}
woodnumber %>% 
  left_join(woodamount, by="Feature_type")
```

How much area does the average wood piece take up?
```{r wood size, eval = FALSE, echo = TRUE}
lw_data%>%
  select(Area_m2,Quantity) %>% 
  mutate(wood_size=as.numeric(Area_m2)/as.numeric(Quantity)) %>% 
  summarize(mean_wood_size=mean(wood_size))
```