# Graphs

The graphs below show the breakdown of my initial data.

## Fires by different landcover characteristics

```{r plotly, eval = TRUE, echo = FALSE, warning=FALSE}
library("plotly") # load
```
We can see of each fire by it's severity, slope and wood generation values.
```{r 3d, eval = TRUE, echo = TRUE, warning=FALSE}
fires %>% 
  plot_ly(x =fires$Severity, y=fires$Per_conifer, z=fires$Avg_slope, color= fires$Class, colors = c('#BF382A', '#0C4B8E','#4AC6B7', '#1972A4', '#965F8A','#FF7070', '#C61951'), 
               size =as.numeric(fires$Acreage),text=fires$Fire_Name,
               marker = list(symbol = 'circle', sizemode = 'diameter'), sizes = c(5, 50)) %>% 
  layout(scene = list(xaxis = list(title = '% Moderate/High Severity'),
                                   yaxis = list(title = '% Conifer'),
                                   zaxis = list(title = '% Slope>23?')))
```

We can see of each fire by it's severity, slope and wood generation values.                                                                    

##  Predictor Variable Representation
```{r fmsb, eval = TRUE, echo = FALSE}

library(fmsb)
```

```{r predictor, eval = TRUE, echo = TRUE}
slope<-fires %>% 
  group_by(Slope) %>% 
  tally()
names(slope)[1] <- "Predictor"
burn<-fires %>% 
  group_by(Burn) %>% 
  tally()
names(burn)[1] <- "Predictor"
trees<-fires %>% 
  group_by(Trees) %>% 
  tally()
names(trees)[1] <- "Predictor"
data<-rbind(slope,burn,trees) %>% 
  pivot_wider(names_from = Predictor, values_from= n)
maxpredictor<-max(data)
data <- rbind(rep(maxpredictor,10) , rep(0,10) , data)
radarchart(data,pfcol=rgb(0.2,0.5,0.5,0.5))
```

In this spider plot, we can see which predictor variable characteristics most fires have.

## Density graph of size of wood features
```{r wood area, eval = TRUE, echo = TRUE}
lw_data %>% 
  mutate(Feature_type = case_when(
    Quantity=="1" ~ "Individual Piece",
    TRUE ~ "Wood Jam")) %>%
  ggplot(mapping = aes(x=as.numeric(Area_m2),fill= Feature_type))+
           geom_density()+
    labs(x = "Size of wood pieces (m2)-log10", y="Density", fill="Wood Feature Type")+
   scale_x_log10()+
   theme_dark()+
    ggtitle("Size variation in in-stream wood")+
  theme(plot.title = element_text(hjust = 0.5))
```

This graph shows the majority of wood features are between 1-2 m2. But by divying it up we can see that wood features that constitute wood jams are on average 10 m2.

## Wood features by Setting
```{r by setting, eval = TRUE, echo = TRUE}
lw_data %>% 
  ggplot(mapping = aes(x=Setting, fill=Setting))+
           geom_bar()+
            theme_linedraw()+
           theme(legend.position = "bottom") +
            labs(x = "Sources of Wood", y="Count")+
        ggtitle("The amount of wood features from each source")+
        theme(plot.title = element_text(hjust = 0.5))
```

We can see from this graph that most wood features arrive in the stream channel from falling in place off the bank.

## Size of wood features in each channel location
```{r size by location, eval = TRUE, echo = TRUE}
lw_data %>% 
  ggplot(mapping = aes(x=Location, y=as.numeric(Quantity), fill=Location))+
           geom_boxplot()+
           scale_y_log10()+
          labs(x = "Location within the channel", y = "Number of Wood Pieces",color = "Age class")+
        ggtitle("Number of Wood Pieces based Channel Location")+
      theme(plot.title = element_text(hjust = 0.5))
```

The more wood pieces, the more likely the feature is to take up the entire channel or at least be in the channel and floodplain.

## Obscured by burn severity
```{r Obscured by severity, eval = TRUE, echo = TRUE}
lw_data %>% 
  ggplot(mapping=aes(fill=Burned, y=Quantity, x=Obscured)) + 
    geom_bar(position="stack", stat="identity")
```

We can see from this plot that more wood is obscured in burned areas.