--- 
title: "Large Wood Impacts on Sediment Transport Following Wildfire"
author: "Alec Arditti"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This shows my work for my Reproducible Data Science Class. I am a graduate student at Utah State University in the Watershed Sciences Department"
---
# Introduction

## Overview of Project

I am mapping woody debris (LW) over time in stream channels following wildfire. This spatial and temporal dataset will be applied in conjunction with geomorphic features to determine the location of sediment routing bottlenecks and which watersheds are more connected. These results will also be compared to an existing post-fire sediment routing model.

## Project Background

This shows my bookdown document for my Reproducible Data Science Class. I am a graduate student at Utah State University in the Watershed Sciences Department


The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
